Object Naming in Language and Vision: A Survey and a New Dataset

### 2020-03-13 papers/LREC2020/analysis.tex
move img
small mods

\begin{figure}
\includegraphics[width=\columnwidth]{figures/types_instances.png}
 \caption{\label{fig:ntypes} Cumulative histograms for number of types in ManyNames, with frequency thresholds} 
\end{figure}

@@

Previous work on object naming has assumed that variation is mostly along a taxonomic axis, and in particular hierarchical (see Section~\ref{sec:rel-work}).
This parameter does not seem to explain the variation in ManyNames. 
Table \ref{tab:rel} shows the distribution of the lexical relations between ManyNames responses and the original \vg annotation, estimated from WordNet.
To obtain these data, we exploited the synset annotation in the \vg names, and added automatic linking for the additional ManyNames names, with a simple first-sense heuristic.%
\footnote{To detect hypernyms, we use the hypernym closure of the synset with a depth of $10$; the other relations are straightforward. The coverage of WordNet for our name data is satisfactory ($90$\%\ of the name types, accounting for $97$\%\ of the tokens).}
As shown in the table, in the vast majority of cases, no hierarchical relation between the name and the synset can be retrieved from WordNet.
Even factoring in the noise introduced by referential uncertainty, it is clear that a good portion of our data cannot be explained by variation in the level of abstraction of the chosen name. 
Among the names that do have a taxonomic relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.
%%In this section, we take a closer look at the lexical variation we observe in our data set. 
%We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
%For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
%In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
%The naming variants can be grouped according to their lexical relation, as follows:
%
%\begin{itemize}
%\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
%\item \textbf{hyponymy}: e.g.\ man vs. person
%\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
%\item \textbf{no relation}: e.g.\  desk vs. apple
%\end{itemize}
%\cs{Shouldn't we mention that we consider only simple move-up hypernymy relations?}

@@

In a qualitative analysis, we found the following types of variation in the data, illustrated with examples in Figure~\ref{fig:ex-high-low-agreement}.
\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \word{toast/dessert}, image C).
\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers as to what an object is (\word{bed/bench}, images J).
\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\word{burger/basket}, image B). 
\textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose synonyms or hypernyms (\word{robe/dress}, image not shown).
%As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
%
\cs{TO ADD: What does ManyNames provide, that WordNet can't: out-of-vocabulary words; we observe instance-based variation, WordNet is class-based: valid (co-)hyponyms, different most preferred name depending on instance, variations which are not due to taxonomic relations}
\begin{table}[t]
%\small
\centering
\setlength{\tabcolsep}{2pt}
\begin{tabular}{lcc|p{2.5cm}}
\toprule
         relation & \% types & \% tokens & \it ex: jacket \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 word-not-covered &  10.6 &  2.6 & \it outdoor vest\\
\midrule
 synonym &  1.1 &  1.1 & \it hoodie  \\
 hyponym &  2.2 &  3.8 & \it parka\\ %, blazer \\
 co-hyponym &  3.1 &  5.9 & \it raincoat\\
 hypernym &  10.5 &  27.7 & \it clothing \\%, coat\\
 rel-not-covered &  72.2 &  58.3 & \it sweatshirt\\%, man\\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets, with examples of variants for \word{jacket}.}
\label{tab:rel}
\vspace{-0.5cm}
\end{table}

>>>>

\begin{figure}
\vspace{-4ex}
\includegraphics[width=\columnwidth]{figures/types_instances.png}
 \caption{\label{fig:ntypes} Cumulative histograms for number of types in ManyNames, with frequency thresholds} 
\end{figure}

@@

Previous work on object naming has assumed that variation is mostly along a taxonomic axis, and in particular hierarchical (see Section~\ref{sec:rel-work}).
This parameter does not seem to explain the variation in ManyNames. 
Table \ref{tab:rel} shows the distribution of the lexical relations between ManyNames responses and the original \vg annotation, estimated from WordNet.
To obtain these data, we exploited the synset annotation in the \vg names, and added automatic linking for the additional ManyNames names, with a simple first-sense heuristic.%
\footnote{To detect hypernyms, we use the hypernym closure of the synset with a depth of $10$; the other relations are straightforward. The coverage of WordNet for our name data is satisfactory ($90$\%\ of the name types, accounting for $97$\%\ of the tokens).}
As shown in the table, in the vast majority of cases, no hierarchical relation between the name and the synset can be retrieved from WordNet.
Even factoring in the noise introduced by referential uncertainty, it is clear that a good portion of our data cannot be explained by variation in the level of abstraction of the chosen name. 
Among the names that do have a taxonomic relation to the synset, hypernyms are the most frequent, meaning that our annotators often chose a more general name than the \vg annotators.
%%In this section, we take a closer look at the lexical variation we observe in our data set. 
%We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
%For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
%In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
%The naming variants can be grouped according to their lexical relation, as follows:
%
%\begin{itemize}
%\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
%\item \textbf{hyponymy}: e.g.\ man vs. person
%\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
%\item \textbf{no relation}: e.g.\  desk vs. apple
%\end{itemize}
%\cs{Shouldn't we mention that we consider only simple move-up hypernymy relations?}

@@

In a qualitative analysis, we found the following types of variation in the data, illustrated with examples in Figure~\ref{fig:ex-high-low-agreement}: 
\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \word{toast/dessert}, image C).
\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers as to what an object is (\word{bed/bench}, image J).
\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\word{burger/basket}, image B). 
\textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose synonyms or hypernyms (\word{robe/dress}, image not shown).
%As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
%
%\cs{TO ADD: What does ManyNames provide, that WordNet can't: out-of-vocabulary words; we observe instance-based variation, WordNet is class-based: valid (co-)hyponyms, different most preferred name depending on instance, variations which are not due to taxonomic relations}
Our analysis 
\begin{table}[t]
%\small
\centering
\setlength{\tabcolsep}{2pt}
\begin{tabular}{lcc|p{2.5cm}}
\toprule
         relation & \% types & \% tokens & \it ex: jacket \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 word-not-covered &  10.6 &  2.6 & \it outdoor vest\\
\midrule
 synonym &  1.1 &  1.1 & \it hoodie  \\
 hyponym &  2.2 &  3.8 & \it parka\\ %, blazer \\
 co-hyponym &  3.1 &  5.9 & \it raincoat\\
 hypernym &  10.5 &  27.7 & \it clothing \\%, coat\\
 rel-not-covered &  72.2 &  58.3 & \it sweatshirt\\%, man\\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets, with examples of variants for \word{jacket}.}
\label{tab:rel}
\vspace{-0.5cm}
\end{table}

### 2020-03-13 papers/LREC2020/intro.tex
small mods

% GBT revision:
In this paper, we present a new dataset, ManyNames, to provide richer possibilities for both analysis and modeling of human naming behavior. 
%We start by surveying existing resources in L\&V that provide object names, assessing their potential to contribute to the study of object naming.
%While these resources can be exploited for this area of inquiry to some extent (as detailed in Section~\ref{sec:survey})\cs{how remove dot?}, we argue that the low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other. 
Existing resources in L\&V that provide object names can be exploited for this area of inquiry to a limited extent only, as we will detail in Section~\ref{sec:survey}\cs{how remove dot?}, because their low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other. 
We chose a creation methodology for ManyNames to overcome these shortcomings in particular.
%This motivates the development of ManyNames, as well as our design choices for it.

% SUBMITTED VERSION:
% Compared to experimental work on perception and language grounding, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
% For instance, picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
% Consequently, a reliable assessment of inter-annotator agreement, speaker preferences, and a deeper linguistic analysis of the observed variation is mostly not possible with available data collections in  L\&V.
% At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
% A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
ManyNames~v.1 contains $36$ crowd-sourced names for $25$K object instances from \vgenome \cite{krishna2016visualgenome}.%
\footnote{Available at \url{https://github.com/amore-upf/manynames}.}
It is inspired in picture naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
%\gbt{Is it ``picture naming norms'', or ``naming norms''?}
% Naming norms record naming responses for dozens or hundreds of speakers for the same object.
Picture naming norms are typically small ($500$-$1$K~images) and use idealized drawings (Figure~\ref{fig:cake}, right; but see, e.g.,~\cite{brodeur2014bank} for exceptions); ManyNames is much larger and uses real-world images of objects in complex visual contexts, which makes it suitable for research in L\&V.
%\gbt{should we add footnote citing the naming norms that have real images? (See commented-out tex; \cite{brodeur2014bank} is the ref for the BOSS database.)}
%\cs{see the addition in ref to Figure}

@@

\begin{figure}[tbp]
\scriptsize
\begin{tabular}{p{4.3cm}p{2cm}}
%VisualGenome+ManyNames & \cite{snodgrass}\\
\centering
\includegraphics[scale=0.15]{figures/2390077_1254219_supercat_unique.png} &
\includegraphics[scale=0.4]{figures/snodgrass_vanderwart_cake_042.png}\\
 cake\ (53),  food\ (19), bread\ (8), burger\ (6), dessert\ (6), snacks\ (3), muffin\ (3),  pastry\ (3) & \hspace{.9cm} cake (83)
\end{tabular}
\caption{Names for a cake object in ManyNames (left) and in Snodgrass's Naming Norms (right), percentages of responses in parentheses.}
\label{fig:cake}
\end{figure}

>>>>

% GBT revision:
In this paper, we present a new dataset, ManyNames, to provide richer possibilities for both analysis and modeling of human naming behavior. 
%We start by surveying existing resources in L\&V that provide object names, assessing their potential to contribute to the study of object naming.
%While these resources can be exploited for this area of inquiry to some extent (as detailed in Section~\ref{sec:survey})\cs{how remove dot?}, we argue that the low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other. 
Existing resources in L\&V that provide object names can be exploited for this area of inquiry to a limited extent only, as we will detail in Section~\ref{sec:survey}, because their low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other. 
We chose a creation methodology for ManyNames that overcome these shortcomings in particular.
%This motivates the development of ManyNames, as well as our design choices for it.

% SUBMITTED VERSION:
% Compared to experimental work on perception and language grounding, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
% For instance, picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
% Consequently, a reliable assessment of inter-annotator agreement, speaker preferences, and a deeper linguistic analysis of the observed variation is mostly not possible with available data collections in  L\&V.
% At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
% A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
ManyNames~v.1\footnote{Available at \url{https://github.com/amore-upf/manynames}.} contains $36$ crowd-sourced names for $25$K object instances from \vgenome \cite{krishna2016visualgenome}. 
It is inspired by picture naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
%\gbt{Is it ``picture naming norms'', or ``naming norms''?}
% Naming norms record naming responses for dozens or hundreds of speakers for the same object.
Picture naming norms are typically small ($500$-$1$K~images) and use idealized drawings (Figure~\ref{fig:cake}, right; but see, e.g.,~Brodeur et al.,~\shortcite{brodeur2014bank} for exceptions); ManyNames is much larger and uses real-world images of objects in complex visual contexts, which makes it suitable for research in L\&V.
%\gbt{should we add footnote citing the naming norms that have real images? (See commented-out tex; \cite{brodeur2014bank} is the ref for the BOSS database.)}
%\cs{see the addition in ref to Figure}

@@

\begin{figure}[tbp]
\scriptsize
\begin{tabular}{p{4.3cm}p{2cm}}
%VisualGenome+ManyNames & \cite{snodgrass}\\
\centering
\includegraphics[scale=0.14]{figures/2390077_1254219_supercat_unique.png} &
\includegraphics[scale=0.4]{figures/snodgrass_vanderwart_cake_042.png}\\
 cake\ (53),  food\ (19), bread\ (8), burger\ (6), dessert\ (6), snacks\ (3), muffin\ (3),  pastry\ (3) & \hspace{.9cm} cake (83)
\end{tabular}
\caption{Names for a cake object in ManyNames (left) and in Snodgrass's Naming Norms (right), percentages of responses in parentheses.}
\label{fig:cake}
\end{figure}

### 2020-03-13 papers/LREC2020/survey.tex
small mods

Both \refcoco and \refcocop \cite{Yu2016} use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco}, 
a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object. 
The matcher must click on the object she thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which results in longer and more complex REs than just the object name, and (ii) in \refcocop the players cannot use location words, urging them to refer to the appearance of objects.
 % \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories? How did you compute these numbers, are they for names, or whole REs?} \sz{well, 80 categories doesn't mean much as the categories can be very general (like "human") ... and it nicely shows that natural names are much more variable than strict categories}
% Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.

Table~\ref{tab:compare} shows that the multiple annotations ($2.8$~on average) actually contain a considerable amount of variation in naming (almost~$2$ different names on average per object). 
%However, the small number of annotations per object does not allow for a reliable assessment of speaker agreement. 
However, the small number of annotations per object does not allow to reliably infer object-specific naming preferences or assess speaker agreement. \cs{double-check formulation}

@@

\begin{figure}
\begin{center}
%\fbox{\parbox{6cm}{
%This is a figure with a caption.}}
\includegraphics[scale=0.25]{figures/vulture.png} 
\begin{tabular}{lp{6cm}}
object id & linked region descriptions\\
\hline
3595788 & the \textbf{bird} is black in color, nose of the \textbf{bird}, a \textbf{bird} relaxing in stand, small white beak of \textbf{bird}, large black talon of \textbf{bird}, a \textbf{bird} on a green pole, a green bar under \textbf{bird}, black \textbf{bird} on green rail, small black eye of \textbf{bird}\\
2286017 & large black \textbf{vulture} on fence, a vulture on bar\\
%2385747 & small white beak of \textbf{bird}\\
2681429 & a semi \textbf{long beak}\\  
2346210 & a black and gray \textbf{vulture}\\
 \end{tabular}
\caption{Bounding boxes, names and region descriptions for an object in VisualGenome}
\label{fig:bird}
\end{center}
\end{figure}

>>>>

Both \refcoco and \refcocop \cite{Yu2016} use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco}, 
a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object. 
The matcher must click on the object she thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which results in longer and more complex REs than just the object name, and (ii) in \refcocop the players cannot use certain location words, urging them to refer to the appearance of objects.
 % \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories? How did you compute these numbers, are they for names, or whole REs?} \sz{well, 80 categories doesn't mean much as the categories can be very general (like "human") ... and it nicely shows that natural names are much more variable than strict categories}
% Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.

Table~\ref{tab:compare} shows that the multiple annotations ($2.8$~on average) actually contain a considerable amount of variation in naming (almost~$2$ different names on average per object). 
%However, the small number of annotations per object does not allow for a reliable assessment of speaker agreement. 
However, the small number of annotations per object does not allow to reliably infer object-specific naming preferences or assess speaker agreement.

@@

\begin{figure}
\begin{center}
%\fbox{\parbox{6cm}{
%This is a figure with a caption.}}
\includegraphics[scale=0.2]{figures/vulture.png} 
\begin{tabular}{lp{6.2cm}}
object id & linked region descriptions\\
\hline
3595788 & the \textbf{bird} is black in color, nose of the \textbf{bird}, a \textbf{bird} relaxing in stand, small white beak of \textbf{bird}, large black talon of \textbf{bird}, a \textbf{bird} on a green pole, a green bar under \textbf{bird}, black \textbf{bird} on green rail, small black eye of \textbf{bird}\\
2286017 & large black \textbf{vulture} on fence, a vulture on bar\\
%2385747 & small white beak of \textbf{bird}\\
2681429 & a semi \textbf{long beak}\\  
2346210 & a black and gray \textbf{vulture}\\
 \end{tabular}
\caption{Bounding boxes, names and region descriptions for an object in VisualGenome}
\label{fig:bird}
\end{center}
\end{figure}
